\documentclass[a4paper,14pt, unknownkeysallowed]{extreport}

\include{packages}

\title{Домашнее задание с 3-го семинара}
\author{Лысцев Никита ИУ7-63Б}
\date{28 февраля 2024}

\begin{document}
	\maketitle
	
\section*{Задание}

\subsection*{Write or speak about your future profession using the following questions as your plan.}

\begin{enumerate}
	\item What is your future profession (job title)?
	\item What qualifications are you going to have?
	\item What courses have you done (are doing now, will be doing in your 4-th
	year)?
	\item What personal qualities are needed to become a good specialist in your field?
	\item What technical skills do you expect to gain during your studies at
	university?
	\item What future possibilities do you see of upgrading your skill set?
	\item What type of practical tasks have you dealt with or would like to deal with?
	\item Have you done (are you going to do) any research (project)? In which
	area?
	\item Have you already had any work experience? Where? When? What did your job involve?
	\item Where would you like to work?
\end{enumerate}

\section*{Ответы}

\begin{enumerate}
	\item My future profession is a Software Engineer.
	
	\item I plan to have a Bachelor's degree in Computer Science or a related field. Additionally, I aim to acquire certifications in relevant programming languages and technologies.
	
	\item Currently, I am enrolled in various computer science courses focusing on algorithms, data structures, software development methodologies, and programming languages such as Java, Python, and C++. In my fourth year, I plan to delve deeper into specialized areas like machine learning, artificial intelligence, and cybersecurity.
	
	\item Personal qualities essential for a successful software engineer include problem-solving skills, attention to detail, creativity, adaptability, patience, and the ability to work both independently and in teams. Effective communication and time management are also crucial for collaborating with colleagues and meeting project deadlines.
	
	\item During my university studies, I expect to gain proficiency in programming languages, understanding of software development principles, knowledge of database management systems, familiarity with various development tools and environments, and experience in debugging and troubleshooting software.
	
	\item I foresee multiple possibilities for upgrading my skill set, including attending workshops, participating in hackathons, pursuing advanced certifications, completing online courses, and engaging in continuous self-learning to stay updated with emerging technologies and industry trends.
	
	\item I have dealt with practical tasks such as developing web applications, creating mobile apps, implementing algorithms, designing databases, and optimizing code for efficiency. In the future, I aspire to work on projects involving machine learning algorithms, cybersecurity solutions, or software systems for automation and optimization.
	
	\item I am currently involved in a research project exploring the application of machine learning algorithms in natural language processing. This research aims to enhance the understanding and interpretation of complex textual data for various applications such as sentiment analysis, language translation, and information retrieval.
	
	\item While I haven't had formal work experience yet, I have undertaken internships and freelance projects where I developed software solutions for small businesses and participated in collaborative coding projects with peers. These experiences have provided me with practical exposure to real-world software development processes and enhanced my problem-solving skills.
	
	\item I would like to work in a dynamic and innovative environment, such as a tech startup, a leading software company, or a research institution where I can contribute to cutting-edge projects and collaborate with talented individuals to solve challenging problems. Additionally, I am open to remote work opportunities that offer flexibility and allow me to work with teams from diverse backgrounds and locations.
\end{enumerate}

	

\end{document}
